\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}

\title{\textbf{AI-Based PC Build Recommendation Engine}}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Overview}

This project presents an intelligent \textbf{PC Build Recommendation Engine} powered by \textbf{Google OR-Tools (CP-SAT Solver)}. The system automates the process of selecting balanced gaming PC components based on budget, hardware compatibility, and performance optimization principles used by professional system builders.

\section*{Objective}

To generate \textbf{bottleneck-free, tier-correct gaming PC builds} that scale realistically with budget while maintaining electrical safety, platform compatibility, and performance efficiency.

\section*{System Architecture}

\begin{itemize}[noitemsep]
    \item \textbf{Data Layer:} CSV datasets containing CPU, GPU, Motherboard, and RAM specifications.
    \item \textbf{Processing Layer:} Data cleaning, normalization, and feature extraction (clocks, cache, latency, TDP).
    \item \textbf{Constraint Engine:} Compatibility and quality rules encoded into a CP-SAT optimization model.
    \item \textbf{Optimization Layer:} Solver maximizes gaming performance under constraints.
    \item \textbf{Output Layer:} Final component list, cooling type, and PSU recommendation.
\end{itemize}

\section*{Key Optimization Rules}

\begin{itemize}[noitemsep]
    \item CPU–Motherboard socket compatibility
    \item CPU–RAM generation matching (DDR4/DDR5)
    \item GPU–CPU tier pairing to avoid bottlenecks
    \item Motherboard class scaling with budget tier
    \item RAM capacity scaling (16GB → 32GB → 64GB)
    \item RAM latency prioritization (lower CAS latency preferred)
    \item PSU sizing based on system power draw
    \item Cooling selection based on thermal environment and budget
\end{itemize}

\section*{Performance Modeling}

CPU performance score is derived from:
\begin{itemize}[noitemsep]
    \item L3 Cache size
    \item Boost clock frequency
    \item Lithography (process node)
    \item Simultaneous Multithreading (SMT)
\end{itemize}

GPU performance score is based on VRAM and clock metrics. The solver maximizes overall gaming performance while penalizing inefficient component choices.

\section*{Technologies Used}

\begin{itemize}[noitemsep]
    \item Python 3
    \item Google OR-Tools (CP-SAT Solver)
    \item pandas and NumPy for data processing
\end{itemize}

\section*{Conclusion}

The system successfully models real-world PC building expertise as a mathematical optimization problem, producing realistic, performance-balanced gaming builds automatically.

\end{document}
